\documentclass{article}

\title{Software Requirements Specification (SRS) \\ AI Air Pollution Prediction \& Visualization System}
\author{Ezequiel Flores, Ashley Jones, Joseph Vazquez, Kevin Antezana}
\date{Snapshot 1}

\begin{document}

\maketitle

\tableofcontents

\section*{Version Description}
\begin{tabular}{|c|c|c|}
\hline
Version & Description & Date \\
\hline
1.0 & Initial SRS for Snapshot 1 & \today \\
\hline
\end{tabular}

\section{Introduction}

\subsection{Purpose}
This document defines the requirements for an AI-based system that predicts air pollution levels and presents data visualizations to users.

\subsection{Intended Audience}
Professor, development team, testers, and project stakeholders.

\subsection{Overview}
This SRS describes the system requirements, interfaces, constraints, and ethical considerations needed to develop the pollution prediction system.

\section{External Interface Requirements}

\subsection{User Interface}
The user interacts with the system through a web-based dashboard.  
The interface allows users to:
\begin{itemize}
    \item Upload air quality datasets
    \item Generate predictions using the AI model
    \item View charts and graphs of pollution trends
    \item Navigate between dashboard pages
\end{itemize}

\subsection{Software Interfaces}
The system depends on:
\begin{itemize}
    \item Python 3.x
    \item Pandas, NumPy, Scikit-Learn for data analysis and machine learning
    \item Matplotlib / Plotly for visualization
    \item Streamlit or Flask for UI framework
    \item CSV or database interface for dataset handling
\end{itemize}

\section{Legal and Ethical Considerations}
The system must handle environmental datasets responsibly and avoid misuse of predictions.  
Uploaded data must comply with privacy and environmental regulations.  
Predictions should not be relied on for legal, medical, or emergency decision-making without expert review.  
Future updates will include data protection safeguards.

\section{Glossary}
\begin{itemize}
    \item AI – Artificial Intelligence
    \item ML – Machine Learning
    \item UI – User Interface
    \item API – Application Programming Interface
    \item PM2.5 – Fine particulate matter
\end{itemize}

\end{document}
